Paper_analyses

### 2021-07-28 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd
one more
check

Quick check that things make sense
```{r}
tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= ground_arousal_lab, color = ground_arousal_lab), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=ground_arousal_lab, color = ground_arousal_lab), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_self_valence)

@@

# higher samp[le rate]

tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  mutate(mediansplit_sample_valence2 = 
           if_else(ValenceMeanThisSample >= 
                     median(ValenceMeanThisSample,
                            na.rm = TRUE), 
                   "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >=
                                                  median(ArousalMeanThisSample,
                                                         na.rm = TRUE), "High", "Low"))

@@

@@

plots_timecourse$eff_size_pup_velocity + 
  p$graphstyle +
    guides(colour = guide_legend(override.aes = list(size=2)))+ #the line size of the legend tends to be smaller in print
  scale_x_continuous(limits = c(0,6), breaks = c(0,2,4,6))+
  scale_y_continuous(limits = c(-1,1.5), breaks = c(-0.5, 0,0.5,1))

    # valence - no significance

    # scale_fill_brewer()

?annotate

>>>>

Quick check that things make sense
```{r}

# higher sample rate]

tmp.df4_full_stim_downs_jun2021_60bins<- tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  mutate(mediansplit_sample_valence2 = 
           if_else(ValenceMeanThisSample > 
                     median(ValenceMeanThisSample,
                            na.rm = TRUE), 
                   "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >
                                                  median(ArousalMeanThisSample,
                                                         na.rm = TRUE), "High", "Low"))

tmp.df4_full_stim_downs_jun2021_with_beh %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= ground_arousal_lab, color = ground_arousal_lab), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=ground_arousal_lab, color = ground_arousal_lab), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_self_valence)

@@

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_sample_valence2)

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_sample_valence2, color = mediansplit_sample_valence2), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=, color = mediansplit_sample_valence2), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~ mediansplit_sample_arousal2)

# what causes 
tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_sample_valence2, color = mediansplit_sample_valence2), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=, color = mediansplit_sample_valence2), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)
   facet_grid(~ mediansplit_sample_arousal2)

   tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(color = mediansplit_sample_arousal2), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=stimIAPS, color = mediansplit_sample_arousal2), size = .6, se = F)+
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
     # geom_text(aes(label = ssid))+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
     geom_text(aes(label = stimIAPS))
   facet_grid(~ mediansplit_sample_valence2)

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(!is.na(ground_arousal_lab))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  # stat_smooth(aes(color = mediansplit_ground_arousal), fun = mean,geom = "line",
  #              se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=stimIAPS, color = ground_arousal_lab), size = .6, se = F)+
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
     # geom_text(aes(label = ssid))+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
     # geom_text(aes(label = stimIAPS))+
   facet_grid(~ ground_valence_lab)

# - use IAPS data to split valence - positive negative
# - within that - compute arousal low mid high within each valence both for the iaps data and my study
# do this on a participant basis or sampleÇ? try sample first
tmp.df4_full_stim_downs_jun2021_60bins %>%
  ungroup()%>%
  mutate(mediansplit_sample_valence2 = 
           if_else(ValenceMeanThisSample > 
                     median(ValenceMeanThisSample,
                            na.rm = TRUE), 
                   "More positive", "More negative"))%>%
  mutate(mediansplit_sample_arousal2 = if_else(ArousalMeanThisSample >
                                                  median(ArousalMeanThisSample,
                                                         na.rm = TRUE), "High", "Low"))

@@

# i =1
# unique(tmp.df4_full_stim_downs_jun2021_60bins$)
for (b in 1:length(nbins)) {
  # for (s in 1:length(nsim)) {

@@

plots_timecourse$eff_size_pup_velocity<- plots_timecourse$eff_size_pup_velocity + 
  p$graphstyle +
    guides(colour = guide_legend(override.aes = list(size=2)))+ #the line size of the legend tends to be smaller in print
  scale_x_continuous(limits = c(0,6), breaks = c(0,2,4,6))+
  scale_y_continuous(limits = c(-1,1.5), breaks = c(-0.5, 0,0.5,1))

plots_timecourse$eff_size_pup_velocity
plots_timecourse$eff_size_pup_amp
